\documentclass[11pt]{article}
\usepackage[a4paper,landscape,margin=0.5in,footskip=12pt]{geometry}
\usepackage[small,compact]{titlesec}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{parskip}

\setlist{noitemsep}

\newcommand{\TheAuthor}{}
\newcommand{\Author}[1]{\renewcommand{\TheAuthor}{#1}\author{#1}}

\newcommand{\TheTitle}{}
\newcommand{\Title}[1]{\renewcommand{\TheTitle}{#1}\title{#1}}

\Title{Algorithms Midterm Cheatsheet}
\Author{Yongun Seong}

\pagestyle{fancy}
\fancyhead{}
\fancyfoot[L]{\TheAuthor}
\fancyfoot[C]{\TheTitle}
\fancyfoot[R]{2017-19937}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

\begin{multicols}{4}

\section{Complexity Analysis}

\begin{gather*}
	2^{n} > n^3 > n^2 > \\
	n\log{n} > n > \log{n}
\end{gather*}

\begin{itemize}
	\item \textbf{Logarithmic}: $\log{n}^c$
	\item \textbf{Polynomial}: $n^c$
	\item \textbf{Exponential}: $n^{n^c}, n!$
\end{itemize}

\begin{itemize}
	\item $\mathcal{O}\bigl(g(n)\bigr)$: $n > n_0,\, cg(n) \ge f(n)$
	\item $\Omega\bigl(g(n)\bigr)$: $n > n_0,\, cg(n) \le f(n)$
	\item $\Theta\bigl(g(n)\bigr)$: $\mathcal{O}\bigl(g(n)\bigr) \cap \Omega\bigl(g(n)\bigr)$
	\item $o\bigl(g(n)\bigr)$: $\lim\limits_{n \to \infty} \frac{f(n)}{g(n)} = 0$
	\item $\omega\bigl(g(n)\bigr)$: $\lim\limits_{n \to \infty} \frac{f(n)}{g(n)} = \infty$
\end{itemize}

\section{Recurrence}

\begin{align*}
	T(n) &= T(n-1) + c \\
	&= cn = \Theta(n) \\
	T(n) &= 2T(n/2) + n \\
	&= 2^{k}T(n/2^{k}) + kn = \Theta(n\log{n}) \\
	T(n) &= 2T(n/2) + 1 \\
	&< cn-1 = \mathcal{O}(n)
\end{align*}

\subsection{Master Theorem}

\begin{align*}
	T(n) &= aT(n/b) + f(n) \\
%	h(n) &= n^{\log_{b}{a}} \\
	c_{crit} &= \log_{b}{a}
\end{align*}

\begin{itemize}
	\item \textbf{Dominated by subproblems}: \\
		$f(n) = \mathcal{O}(n^{c_{< c_{crit}}})$ then \\
		$T(n) = \Theta\bigl(n^{c_{crit}})\bigr)$

	\item \textbf{Same}: \\
		$f(n) = \Theta\bigl(n^{c_{crit}} \log^k{n}\bigr)$ then \\
		$T(n) = \Theta\bigl(n^{c_{crit}}\log^{k+1}{n}\bigr)$

	\item \textbf{Dominated by overhead}: \\
		$f(n) = \Omega(n^{c_{> c_{crit}}})$ then if also \\
		$af(n/b) \le (k_{<1})f(n)$ then \\
		$T(n) = \Theta\bigl(f(n)\bigr)$
\end{itemize}

\subsubsection{Examples}

\begin{align*}
	T(n) &= 2T(n/3) + c \\
	\text{(Case 1)} \,
	&= \Theta(n^{\log_3{2}})
	\\
	T(n) &= 2T(n/2) + n \\
	\text{(Case 2)} \,
	&= \Theta(n\log{n})
	\\
	T(n) &= 2T(n/4) + n \\
	\text{(Case 3)} \,
	&= \Theta(n)
\end{align*}

\section{RB Tree}

\begin{enumerate}
	\item Root is black.
	\item Leaf is black.
	\item Red children are black.
	\item All paths have same bh.
\end{enumerate}

\begin{itemize}
	\item $2^{bh(r)} -1$ internal nodes.
	\item $h \le 2 \log_2{n+1}$.
\end{itemize}

\subsection{Insert}

\begin{enumerate}
	\item Insert red.
	\item If $p$ is black, done.
	\item $p^2$ and sibling are black.
	\item $p$ sibling $s$ red: recolor $p^2, p, s$. Recheck $p^2$.
	\item If right child, rotate $p$ left.
	\item Rotate $p^2$ right, recolor.
\end{enumerate}

\subsection{Delete}

\begin{enumerate}
	\item TODO
\end{enumerate}

\section{B-Tree}

\begin{itemize}
	\item Every node except root has $\lfloor k/2 \rfloor \sim k$ keys.
	\item All leaves at same depth.
	\item Height: $\mathcal{O}(\log_k{n})$.
\end{itemize}

\subsection{Insert}

\begin{enumerate}
	\item Just insert.
	\item If overflow, try rotating out to siblings.
	\item Explode and push mid to parent.
	\item Repeat in parent.
\end{enumerate}

Conditions are maintained because parent grows by one, or we create new root,
and root is excempt from conditions.

\subsection{Delete}

\begin{enumerate}
	\item Swap with successor.
	\item Delete value. If underflow:
	\item Try rotating in from siblings.
	\item Merge with sibling.
	\item If parent underflow, repeat.
\end{enumerate}

\section{kD-Tree}

Alternate dimensions by level.

\subsection{Delete}

TODO

\section{Hash Table}

\begin{itemize}
	\item \textbf{Division}: $x \mod{p}$
	\item \textbf{Multiply}: $xA \mod{1} \cdot m$ \\
		$A$ sometimes golden ratio.
\end{itemize}

\begin{itemize}
	\item \textbf{Chaining}: buckets are lists.
	\item \textbf{Linear Probing}: primary clustering, run of occupied
		slots.
	\item \textbf{Quadratic Probing}: secondary clustering, still results
		in long chains.
	\item \textbf{Double Hashing}: $h(k, i) = h_1(k) + ih_2(k)$
	\item \textbf{Load factor}. $\alpha = n/m$.
\end{itemize}

\subsection{Search Time - Chaining}

\begin{itemize}
	\item Average negative search $\Theta(1+\alpha)$.
	\item Average positive search $\Theta(1+\alpha) = 1 + \alpha/2 -
		\alpha/2n$ keys examined.
\end{itemize}

\subsection{Search Time - Open Addressing}

\begin{itemize}
	\item Average negative search $\frac{1}{1-\alpha}$.
	\item Average positive search $\frac{1}{\alpha} \log{\frac{1}{1-\alpha}}$
\end{itemize}

\section{DSU}

\subsection{List}

\begin{itemize}
	\item Linked list with ptr back to head.
	\item Union by concat and replace head ptr.
	\item \textbf{Weighted Union}. Prefer updating shorter list, maintain
		set weight in head.
	\item $m$ make-set, $n$ operations. $\mathcal{O}(m + n\log{n})$.

\end{itemize}

\subsection{Tree}

\begin{itemize}
	\item \textbf{Union by rank}. Prefer modifying shorter tree.
	\item \textbf{Path compression}. Shortcut root ptr during recursive
		return.
	\item $m$ make-set, $n$ operations. $\mathcal{O}(m + \log^{*}{n})$.
\end{itemize}

\end{multicols}

\end{document}
